Stimulated Accretion from Circumgalactic Media Interactions

### 2024-02-15 paper/ms.tex
Remove dilution

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{fig/cumprof.pdf}
  \caption{The cumulative amount of the central's CGM gas accreted onto the disk
  ($r<20\,\kpc$) as a function of time. The blue line shows the case of the
  galaxy merger setup and the orange line shows the case of an isolated galaxy.
  The effect of the merger is to increase the amount of mass accreted onto the
  central. We stress that this plot does not include the mass from the satellite's
  disk or CGM.}
  \label{fig:cumprof}
\end{figure}
